\begin{thebibliography}{99}

%
\bibitem{Artykul}Leena Ukkonen, Lauri Syd\"anheimo and Yahya Rahmat-Samii, \emph{6th European Conference on Antennas and Propagation (EUCAP)}, \emph{Sewed Textile RFID Tag and Sensor Antennas for On-Body Use}, Department of Electronics, Rauma Research Unit, Tampere University of Technology, Finland, Electrical Engineering Department, University of California Los Angeles, IEEE, 2011.
%
\bibitem{RFID_Handbook}Klaus.~Finkenzeller, \emph{RFID Handbook}, John Wiley \& Sons LTD, United Kingdom, 2010.
%
\bibitem{RFID_Systems}Miodrag Bolic, David Simplot-Ryl, Ivan Stojmenovic, \emph{RFID Systems Research trends and challenges}, John Wiley \& Sons LTD, United Kingdom, 2010.
%
\bibitem{RFID_Design}Albert Lozano-Nieto, \emph{RFID Design Fundamentals and Applications}, Taylor and Francis Group, LLC, 2011.
%
\bibitem{Ultrawideband}Jovam.~E.~Lebaric, Richard.~W.~Adler, and Matthew.~E.~Limbert, \emph{Ultrawideband, zero visual RF vest antenna for man-portable radios}, Naval Postgraduate School, Monterey, USA, 2001. 
%
\bibitem{RFID_in_Logistics}Erick C. Jones, Christopher A. Chung, \emph{RFID in Logistics A Practical Introduction}, Taylor and Francis Group, LLC, 2008. 
%
\bibitem{Antennas}Zhi Ning Chen, \emph{Antennas for portable devices}, Institute of InfoComm Research, Singapore, 2007.
%
\bibitem{Effect}Pekka Salonen, Yahya Rahmat-Samii, Marijke Scaffrath, Markku Kivovski, \emph{Effect of textile materials on wearable antenna performance: A case study of GPS Antennas}, in \emph{IEEE Transactions on Antennas and Propagation}, 2004.
%
\bibitem{Technologia}H. Jankowski, Ł. Krzak, M. Szczurkowski, M. Warzecha, C. Worek, \emph{Technologia radiowej identyfikacji obiektów RFID}, Wiadomości Elektroniczne Nr 9/2006 str. 8-14, ISSN 0043-5112.
%
\bibitem{Propagation}Simon R. Saunders, \emph{Antennas and Propagation for Wireless Communication Systems}, 1999. 
%
\bibitem{Handbook_of_RF}F. Dowla, \emph{Handbook of RF and Wireless Technologies}, Elsevier, 2003.
%
\bibitem{RFID_Optimization}Wolf-Ruediger Hansen, Frank Gillert, \emph{RFID for the Optimization of Business Processes}, John Wiley \& Sons LTD, 2008.
%
\bibitem{Pomiary_parametrów}J. Modelski, E. Jaszczyszyn, H. Chaciński, P. Majchrzak, \emph{Pomiary parametrów anten}, Oficyna Wydawnicza Politechniki Warszawskiej, Warszawa 2004.  
%
\bibitem{Fale_i_Anteny}Jarosław Szóstka, \emph{Fale i Anteny}, Wydawnictwo Komunikacji i Łączności Warszawa, 
2001.
%
\bibitem{Kody_kreskowe}\emph{ASKA systemy automatycznej identyfikacji}, \url{www.kodykreskowe.com}
%
\bibitem{REG}\emph{Radio Engineering Group}, \url{www.reg.aei.polsl.pl}
%
\bibitem{Portal_RFID}\emph{Portal RFID Radio Frequency Identyfication}, \url{www.portalrfid.pl}
%
\bibitem{PWSK}\emph{PWSK programy dla firm}, \url{www.pwsk.pl}
%
\bibitem{RFID_lab}\emph{Technologie RFID i EPC}, Portal Tecxhnologiczny Uniwersytetu Ekonomicznego we Wrocławiu, \url{www.rfid-lab.pl}
\end{thebibliography}
